Estimating Gaze Duration Error from Eye Tracking Data

### 2022-09-23 paper/paper.tex
Paper adjustments

Gaze fixation models will typically have an error profile that is dependent on both 
the nature of the media being presented, the variety of faces and lighting conditions 
in the training data. In addition, it has been observed that the error profile varies 
depending on the location of the true fixation point within the subjects field of view.
The errors in fixation point measurement for a given eye tracking solution are routinely
adjusted through a process called calibration. Improvements in the callibration process
are an ongoing focus for the development of algorithms\cite{Zhang2014,Hassoumi2019} 
and software tools\cite{ETCAL2018}

>>>>

Gaze fixation models will typically have an error profile that is dependent on both 
the nature of the media being presented, the variety of faces and lighting conditions 
in the training data. In addition, it has been observed that the error profile varies 
depending on the location of the true fixation point within the subjects field of view.
The errors in fixation point measurement for a given eye tracking solution are routinely
adjusted through a process called calibration. Improvements in the callibration process
are an ongoing focus for the development of algorithms\cite{Zhang2014,Hassoumi2019} 
and software tools\cite{ETCAL2018}. In some scenarios there are additional considerations
such as whether to use fixation data from individual eyes, or a composite 
signal\cite{Hooge2019}.
